\pkg{Rgbp}: An R Package for Gaussian, Poisson, and Binomial Hierarchical Modeling

### 2013-08-29 jss/article.tex
edit3

In Figure \ref{fig:hospitalcoverage}, the black horizontal line at 0.95 represents the nominal confidence level, the smooth red curve connects Rao-Blackwellized (RB) unbiased coverage estimates for 31 hospitals, and the dashed zagged blue curve passes simple unbiased coverage estimates for these hospitals. As the number of simulations increases, the zig-zagging blue curve would be closer to the smooth red curve by the law of large numbers.

>>>>

In Figure \ref{fig:hospitalcoverage}, the black horizontal line at 0.95 represents the nominal confidence level and the smooth red curve connects Rao-Blackwellized (RB) unbiased coverage estimates for 31 hospitals.
